### 2016-01-27 Irregular-occ/Irregular-occ.tex
.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{natbib,twoopt}
\usepackage[breaklinks=true, draft]{hyperref} %% to avoid \citeads line fills
\usepackage{arydshln}
\bibpunct{(}{)}{;}{a}{}{,} %% natbib format for A&A and ApJ
\makeatletter
\newcommandtwoopt{\citeads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citealp[#1][#2]{#3}}}
\newcommandtwoopt{\citepads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citep[#1][#2]{#3}}}
\newcommandtwoopt{\citetads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citet[#1][#2]{#3}}}
\newcommandtwoopt{\citeyearads}[3][][]%
{\href{http://adsabs.harvard.edu/abs/#3}
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citeyear[#1][#2]{#3}}}
\makeatother
\titlerunning{Predictions of stellar occultations by irregular satellites up to 2017}
\authorrunning{Gomes-Júnior et al.}

@@

@@

\begin{figure*}
\begin{centering}
\subfigure[NEP081 JPL and \cite{Emelyanov2015} ephemeris]{\includegraphics[width=8.8cm]{figures/JPL-EME_Triton.eps} \label{Fig:offxtanomxjpl}}
\subfigure[\cite{Zhang2013} and \cite{Emelyanov2015} ephemeris]{\includegraphics[width=8.8cm]{figures/Zhang-EME.eps} \label{Fig:offxtanomxni}}
\caption{Comparison between the ephemeris between the \cite{Emelyanov2015}, \cite{Zhang2013} and JPL ephemeris.}
\label{Fig:offxanom}
\end{centering}
\end{figure*}

@@

\begin{figure*}
\begin{centering}
\includegraphics[scale=0.4]{figures/Pasiphae_2016-04-09T03:58:19.png}   
\caption{Occultation map for Pasiphae regarding to the first event sampled in Table \ref{Tab: occ-list}. The central red dot show the geocentric closest approach of the shadow. The small ones shows the center of the shadow separated by one minute. The lines show the path of the shadow over the Earth.}
\label{Fig: ocultacao}
\end{centering}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{natbib,twoopt}
\usepackage[breaklinks=true]{hyperref} %% to avoid \citeads line fills
\usepackage{arydshln}
\bibpunct{(}{)}{;}{a}{}{,} %% natbib format for A&A and ApJ
\makeatletter
\newcommandtwoopt{\citeads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citealp[#1][#2]{#3}}}
\newcommandtwoopt{\citepads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citep[#1][#2]{#3}}}
\newcommandtwoopt{\citetads}[3][][]{\href{http://adsabs.harvard.edu/abs/#3}%
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citet[#1][#2]{#3}}}
\newcommandtwoopt{\citeyearads}[3][][]%
{\href{http://adsabs.harvard.edu/abs/#3}
{\def\hyper@linkstart##1##2{}%
\let\hyper@linkend\@empty\citeyear[#1][#2]{#3}}}
\makeatother
\titlerunning{Predictions of stellar occultations by irregular satellites up to 2017}
\authorrunning{Gomes-Júnior et al.}

@@

In Fig. \ref{Fig:eph-Phoebe} we compare our ephemeris (PH15) with the SAT375 JPL\footnote{Jacobson, R.A. 2015-Feb-27. "Satellite Ephemeris: SAT375", JPL Satellite Ephemeris File Release, \url{ftp://ssd.jpl.nasa.gov/pub/eph/satellites/nio/LINUX_PC/sat375l.txt}} and the \cite{Emelyanov2007} ephemeris. We can see that our ephemeris is closer to the SAT375 JPL ephemeris where the difference between them is smaller than 20 mas (< 10 mas in Declination). This difference is smaller than the apparent diameter of Phoebe (see Table \ref{Tab: satellite-diameter})

\begin{figure*}
\begin{centering}
\subfigure[SAT375 JPL and PH15 ephemeris]{\includegraphics[width=8.8cm]{figures/Phoebe_JPL-ph15.eps} \label{Fig:eph-Triton-eme}}
\subfigure[\cite{Emelyanov2007} and PH15 ephemeris]{\includegraphics[width=8.8cm]{figures/Phoebe_EME-ph15.eps} \label{Fig:eph-Triton-zhang}}
\caption{Comparison between the PH15, SAT375 JPL and \cite{Emelyanov2007} ephemeris.}
\label{Fig:eph-Phoebe}
\end{centering}
\end{figure*}

@@

For Triton, we used the most recent ephemeris published by \cite{Emelyanov2015}. In Fig. \ref{Fig:eph-Triton} we compare the ephemeris with the ephemeris published in \cite{Zhang2014} and the NEP081 JPL ephemeris \citep{Jacobson2009}. It is possible to see that the difference between the three ephemeris is smaller than 15 mas for the period 2015-2018. This value is smaller than the apparent size of Triton (124 mas, see Table \ref{Tab: satellite-diameter}), which means a good probability of observing an event by this object.

\begin{figure*}
\begin{centering}
\subfigure[NEP081 JPL and \cite{Emelyanov2015} ephemeris]{\includegraphics[width=8.8cm]{figures/JPL-EME_Triton.eps} \label{Fig:eph-Triton-eme}}
\subfigure[\cite{Zhang2014} and \cite{Emelyanov2015} ephemeris]{\includegraphics[width=8.8cm]{figures/Zhang-EME.eps} \label{Fig:eph-Triton-zhang}}
\caption{Comparison between the \cite{Emelyanov2015}, \cite{Zhang2014} and NEP081 JPL \citep{Jacobson2009} ephemeris.}
\label{Fig:eph-Triton}
\end{centering}
\end{figure*}

For Nereid, we used the ephemeris published by \cite{Emelyanov2011}, which is more recent than the JPL ephemeris published by \cite{Jacobson2009}. The comparison between the two ephemeris can be seen in Fig. \ref{Fig:eph-Nereid}. The difference between them is smaller than 60 mas which is bigger than the satellite apparent diameter (see Table \ref{Tab: satellite-diameter}). Although this fact, the difference in bigger in Right Ascension than in Declination, which means that, in an event, the error would be smaller in the latitude where the shadow will pass on Earth than the error at the time of the occultation.

\begin{figure}
\begin{centering}
\includegraphics[width=8.8cm]{figures/JPL-EME_Nereid.eps}
\caption{Comparison between the \cite{Emelyanov2011} and NEP081 JPL \citep{Jacobson2009} ephemeris }
\label{Fig:eph-Nereid}
\end{centering}
\end{figure}

@@

\begin{figure*}
\begin{centering}
\includegraphics[scale=0.4]{figures/Triton_2017-10-05T23:51:53.png}   
\caption{Occultation map for Triton.% regarding to the first event sampled in Table \ref{Tab: occ-list}.
The central red dot show the geocentric closest approach of the shadow. The small ones shows the center of the shadow separated by one minute. The lines show the path of the shadow over the Earth. The shadow moves from right to left.}
\label{Fig: ocultacao}
\end{centering}
\end{figure*}
